%!TEX root = ../thesis_phd.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% acknowledge.tex: Acknowledgements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This work would not have been possible without my family.
My parents, Dorothy and Bill, have always been a great support.
They raised me to adulthood and ensured I could always pursue
my dreams.
My brother, Joseph, is my oldest friend.
The lives we live today are an imprint of the experiences we have shared.
I owe the utmost gratitude to Michelle, who has been my closest ally
throughout recent years.
There is no way I could have completed this work without her support,
both material and emotional.

I will always remember the other graduate students who
started this journey with me; in particular
Terry Bretz-Sullivan, Barry Costanzi, Mark Pepin, Bern Youngblood,
Tanner Prestergard, Michael Janas, and Tobias Gulden.
Working through coursework with them was both enlightening and
enjoyable.
I have also enjoyed the friendship of Alexander Gude and Charles McEachern,
who happened to start on the road before me, but were there all the same.

My fellow graduate students in the Minnesota neutrino group --
Susan Lein, Nick Raddatz, Kanika Sachdev, and Jan Zirnstein  --
were a constant resource.
The openness we encouraged created an environment for us all to succeed;
the conversations we shared were instrumental to my development;
the laugher we enjoyed was the ultimate diversion.
I cannot imagine a better group with whom to have taken this journey.

This opportunity would not have existed without the Minnesota neutrino group
as a whole, especially my advisor Gregory Pawloski.
I would also like to thank Ken Heller for bringing me on in the first place,
and Marvin Marshak for making the experience relatable.
Navigating through this environment would have been considerably more
difficult without the shrewd lessons and caring guidance of Jody Kaplan.
Toward the end of my time as a student, I learned learned a great deal from
conversations from Justin Hietala, who became a cherished friend despite the
short time we worked together.

Of course, none of this work would have been possible without the \nova
collaboration; especially the leadership and vision of Gary Feldman,
Mark Messier, and Ryan Patterson.
I would like to thank Christopher Backhouse and Gavin Davies
for the vast knowledge which they shared freely.
I would also like to recognize the graduate students from
other institutions with whom I have learned, particularly
Evan Niner, Michael Baird, and Fernanda Psihas.

Finally, I owe the many thanks to Alexander Radovic and Adam Aurisano
for breathing life into this project at just the right moment.
The success demonstrated in this dissertation
would not have been achieved without their effort.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
